Exposing Bugs in JavaScript Engines through Test Transplantation and Differential Testing

### 2020-06-13 paper/paper.tex
done with my pass on section 5

Fuzzers are typically categorized in two main groups--those that build
inputs anew (generational) and those that modify existing inputs
(mutational). We used two black-box mutational
fuzzers\Comment{Radamsa~\cite{radamsa} and QuickFuzz~\cite{quickfuzz}}
in this study. In the following, we provide rationale for this
selection.

Generational fuzzers are typically grammar-based. These fuzzers
generate a new file using the grammar of the language whose inputs
should be fuzzed. Intuitively, those fuzzers implement a traversal of
the production rules of the input grammar to create syntax trees,
which are then pretty-printed. Consequently, this approach produces
inputs that are syntactically valid by construction. We analyzed four
grammar-based fuzzers--Grammarinator~\cite{grammarinator},
jsfunfuzz~\cite{jsfunfuzz},
LangFuzz~\cite{Holler:2012:FCF:2362793.2362831}, and
Megadeth~\cite{grieco2016quickfuzz}.  Unfortunately, none of those
were effective out of the box. For example, we produced 100K inputs
with Grammarinator and only few inputs were valid. With Megadeth, we
were able to produce more\Comment{ \Fix{Y, Y$>$Y?}} valid inputs as it
contains some heuristics to circumvent violations of certain typing
rules.\Comment{ such as \Fix{variable used must be defined?}.}
Nonetheless, running those inputs in our infrastructure we were unable
to find discrepancies. Inspecting those inputs, we realized that they
reflected very simple scenarios. To sum up, a high percentage of inputs
that Grammarinator and Megadeth generated were semantically-invalid
that we needed to discard whereas the valid inputs manifested no
discrepancies. Considering jsfunfuzz~\cite{jsfunfuzz}, we noticed
that, in addition to the issues mentioned above, it produces inputs
that use functions that are only available in the \smonkey{}
engine. We would need either to mock those functions in other engines
or to discard those tests. Considering
LangFuzz~\cite{Holler:2012:FCF:2362793.2362831}, the tool is not
publicly available. Another fundamental issue associated with
generational fuzzers in our context is that the tests they produce do
not contain assertions; to enable the integration of this kind of
fuzzers in our infrastructure---we would need to look for
discrepancies across compiler error messages as opposed to assertion
violations.  All in all, although grammar-based fuzzers have been
shown effective to find real
bugs~\cite{Holler:2012:FCF:2362793.2362831}, we did not consider those
fuzzers in this study for the reasons above.

@@

Mutational fuzzers can be either white-box or black-box. White-box
mutational fuzzers are typically coverage-based. American Fuzz Loop
(AFL)~\cite{afl} and libFuzzer~\cite{libfuzzer} are examples of this
kind of fuzzers. These fuzzers run tests inputs against instrumented
versions of the program under testing with the typical goal of finding
universal errors like crashes and buffer overflows. The instrumentation
adds code to collect branch coverage and to monitor specific
properties\footnote{There are options in the clang toolchain to build
  programs with fuzzing instrumentation~\cite{libfuzzer}. clang
  provides several sanitizers for property
  checking~\cite{clang-documentation}.}. AFL uses coverage to determine
inputs that uncover a new branch and hence should be fuzzed more
whereas libFuzzer uses evolutionary generation--it tries to minimize
the distances to still-uncovered branches of the program. AFL takes
the instrumented program binary (say, a JS engine) and one seed input
to that program (say, a JS program) and produces on output
fault-revealing inputs, if found. Considering our context of
application, we needed to instrument one runtime engine for fuzzing.
We chose \veight\ for that. Unfortunately, we found that most of the inputs produced
by AFL violate the JS grammar. Furthermore, the fuzzing task can take
days for a single seed input and there is no simple way to guide the
exploration\footnote{Exchanged emails with the tool author.}. That
happens because the fuzzer aims to explore the entire decision tree
induced from the engine's main function, including the branches
associated with the higher layers of the compiler (\eg{}, lexer and
parser). It is worth mentioning that Google mitigates that problem
with libFuzzer by asking developers to create fuzz targets for
specific program
functions~\cite{libFuzzer-tutorial-google,libFuzzer-chromium-google}. Although
that approach has shown to be effective, it requires domain knowledge
to create the calling context to invoke the fuzz target. For that, we
decide not to consider coverage-based in this study.

We used two black-box mutational fuzzers in this
study: \radamsa~\cite{radamsa} and \quickfuzz~\cite{quickfuzz}. These
fuzzers require no instrumentation and domain-knowledge. They mutate
existing inputs randomly. The strength of the approach is
limited by the quality of the test suite and the supported mutation
operators, which are typically simple. We chose these specific fuzzers
because, conceptually, one complements the other. \quickfuzz\ creates
mutations like \radamsa. However, in contrast to \radamsa, \quickfuzz\ is aware
of the \js\ syntax; it is able to replace sub-trees of the syntax
tree~\cite{grieco2016quickfuzz} with trees created anew. Notwithstanding,
since \radamsa performs simpler syntactic source code modifications,
it also produces a higher number of valid inputs (when compared with,
for instance, AFL).

>>>>

%% Fuzzers are typically categorized in two main groups--those that build
%% inputs anew (generational) and those that modify existing inputs
%% (mutational).

Fuzzers are tools for generating inputs for a given input
format~\cite{8863940}. Different fuzzing strategies exist. We analyzed
\emph{generational} and \emph{mutational} fuzzers.

Generational fuzzers create inputs anew, typically following a
language description, typically context-free grammars. Intuitively,
those fuzzers implement a traversal of the production rules of a
grammar to create syntax trees, which are then pretty-printed and used
as a fresh input. Such strategy to create inputs produces inputs that
are syntactically valid by construction. We analyzed four
grammar-based fuzzers--Grammarinator~\cite{grammarinator},
jsfunfuzz~\cite{jsfunfuzz},
LangFuzz~\cite{Holler:2012:FCF:2362793.2362831}, and
Megadeth~\cite{grieco2016quickfuzz}.  Unfortunately, none of those
were effective out-of-the-box. For example, we produced 100K inputs
with Grammarinator and only few inputs were semantically valid. With
Megadeth, we were able to produce more\Comment{ \Fix{Y, Y$>$Y?}} valid
inputs as it contains some heuristics to circumvent violations of
certain typing rules.\Comment{ such as \Fix{variable used must be
    defined?}.}  Nonetheless, running those inputs in our
infrastructure we were unable to find discrepancies. Inspecting those
inputs, we realized that they reflected very simple scenarios. To sum
up, a high percentage of inputs that Grammarinator and Megadeth
generated were semantically-invalid that we needed to discard whereas
the valid inputs manifested no discrepancies. Considering
jsfunfuzz~\cite{jsfunfuzz}, which has been developed by the Mozilla
team, we noticed that, in addition to the issues mentioned above, it
produces inputs that use functions that are only available in the
\smonkey{} engine. We would need either to mock those functions in
other engines or to discard those tests. Considering
LangFuzz~\cite{Holler:2012:FCF:2362793.2362831}, the tool is not
publicly available. Another fundamental issue associated with
generational fuzzers in our context is that the tests they produce do
not contain assertions; to enable the integration of this kind of
fuzzers in our infrastructure---we would need to look for
discrepancies across compiler error messages as opposed to assertion
violations.  All in all, although grammar-based fuzzers have been
shown effective to find real
bugs~\cite{Holler:2012:FCF:2362793.2362831}, we did not consider those
fuzzers in this study for the reasons above.

@@

Mutational fuzzers modify inputs files provided as seeds. Gray-box
mutational fuzzers use coverage information to guide the mutation
process. American Fuzz Loop (AFL)~\cite{afl} and
libFuzzer~\cite{libfuzzer} are the most popular coverage-guided
fuzzers of today. These fuzzers run tests inputs against instrumented
versions of the programwith the typical goal of finding universal
errors, like crashes and buffer overflows. The instrumentation adds
code to collect branch coverage and to monitor specific
properties\footnote{There are options in the clang toolchain to build
  programs with fuzzing instrumentation~\cite{libfuzzer}. clang
  provides several sanitizers for property
  checking~\cite{clang-documentation}.}. AFL and libFuzzer work very
similarly. They use coverage to find inputs that uncover a new branch
and hence should be fuzzed more. These tools take as input a program
binary (say, a JS engine), which is instrumented to collect coverage
information and to capture runtime violations (\eg{}, illegal memory
accesses), and one seed input to that program (say, a JS program) and
produces on output fault-revealing inputs. We chose to use AFL and
instrument \veight. Unfortunately, we found that most of the inputs
produced by AFL violate the JS grammar. We would need to translate
production rules of Python to the AFL format to circumvent that
issue. We found that the fuzzing task can take days for a single seed
input and there is no clear way to guide the exploration. That happens
because the fuzzer aims to explore the entire decision tree induced
from the engine's main function, including the branches associated
with the higher layers of the compiler (\eg{}, lexer and parser). One
way to mitigate that problem is by writing fuzzing targets
(a.k.a. targets) for specific program functions. Although that
approach has shown to be effective at
Google~\cite{libFuzzer-tutorial-google,libFuzzer-chromium-google}, it
requires domain knowledge to create the calling context to invoke the
fuzz target. For that, we decide not to consider coverage-based in
this study.

We used two black-box mutational fuzzers in this
study: \radamsa~\cite{radamsa} and \quickfuzz~\cite{quickfuzz}. These
fuzzers require no instrumentation and domain-knowledge. They mutate
existing inputs randomly. The strength of the approach is
limited by the quality of the test suite and the supported mutation
operators, which are typically simple. We chose these specific fuzzers
because, conceptually, one complements the other. \quickfuzz\ creates
mutations like \radamsa. However, in contrast to \radamsa, \quickfuzz\ is aware
of the \js\ syntax; it is able to replace sub-trees of the syntax
tree~\cite{grieco2016quickfuzz} with trees created anew. Notwithstanding,
since \radamsa performs simpler syntactic source code modifications,
it also produces a higher number of valid inputs.
